### 2021-02-11 README.Rmd
codecov badge on README

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/open-AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/open-AIMS/dataaimsr/actions)
![pkgdown](https://github.com/open-AIMS/dataaimsr/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
[![Ask Us Anything
\!](https://img.shields.io/badge/Ask%20us-anything-1abc9c.svg)](https://github.com/open-AIMS/dataaimsr/issues/new)
![Open Source
Love](https://badges.frapsoft.com/os/v2/open-source.svg?v=103)
<!-- badges: end -->

@@

`dataaimsr` is the **AIMS Data Platform R Client**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://open-aims.github.io/data-platform).

@@

**AIMS Data Platform** requires an API Key for requests, [get a key here.](https://open-aims.github.io/data-platform/key-request)

@@

The **AIMS Data Platform API** is a *REST API* providing *JSON* formatted data. Documentation about available data sets can be found on the [AIMS Data Platform API](https://open-aims.github.io/data-platform).

@@

Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://open-aims.github.io/dataaimsr).

>>>>

<!-- badges: start -->
[![Lifecycle: maturing](https://img.shields.io/badge/lifecycle-maturing-blue.svg)](https://www.tidyverse.org/lifecycle/#maturing)
[![R build status](https://github.com/open-AIMS/dataaimsr/workflows/R-CMD-check/badge.svg)](https://github.com/open-AIMS/dataaimsr/actions)
[![Codecov test coverage](https://codecov.io/gh/open-AIMS/dataaimsr/branch/master/graph/badge.svg)](https://codecov.io/gh/open-AIMS/dataaimsr?branch=master)
![pkgdown](https://github.com/open-AIMS/dataaimsr/workflows/pkgdown/badge.svg)
[![license](https://img.shields.io/badge/license-MIT + file LICENSE-lightgrey.svg)](https://choosealicense.com/)
[![packageversion](https://img.shields.io/badge/Package%20version-`r version`-orange.svg)](commits/master)
[![Ask Us Anything
\!](https://img.shields.io/badge/Ask%20us-anything-1abc9c.svg)](https://github.com/open-AIMS/dataaimsr/issues/new)
![Open Source
Love](https://badges.frapsoft.com/os/v2/open-source.svg?v=103)
<!-- badges: end -->

@@

`dataaimsr` is the **AIMS Data Platform R package**, and will provide you with easy access to data sets from the [AIMS Data Platform API](https://open-AIMS.github.io/data-platform).

@@

**AIMS Data Platform** requires an API Key for requests, [get a key here.](https://open-AIMS.github.io/data-platform/key-request)

@@

The **AIMS Data Platform API** is a *REST API* providing *JSON* formatted data. Documentation about available data sets can be found on the [AIMS Data Platform API](https://open-AIMS.github.io/data-platform).

@@

Further information about `dataaimsr` and the **AIMS Data Platform API** can be seen on the [project page](https://open-AIMS.github.io/dataaimsr).
